\section*{Exam 3: Functional Analysis (Giải tích hàm)}

\noindent
\begin{minipage}[t]{0.45\textwidth}
\begin{center}
SAIGON UNIVERSITY\\[0.2cm]
\textbf{EXAM PAPER NO. 3}\\[0.2cm]
\end{center}
Semester: II........................................................\\
Training Level: Undergraduate ...........................\\
Student Name:...........................................
\end{minipage}
\hfill
\begin{minipage}[t]{0.5\textwidth}
\begin{center}
\textbf{FINAL EXAMINATION}\\[0.1cm]
\textbf{Course: Functional Analysis}\\[0.1cm]
\textbf{Course Code: 801047}\\[0.1cm]
\textit{Duration: 90 minutes (not including time to distribute papers)}
\end{center}
Academic Year: 2025-2026.....................................\\
Training Form: Full-time ......................\\
Student ID:.............................................
\end{minipage}
\vspace{0.3cm}

\hrule
\vspace{0.3cm}
\begin{center}
Students \textbf{CANNOT} use materials. Invigilators provide no further explanations.
\end{center}
\vspace{0.3cm}

\noindent \textbf{Problem 1 (3.0 points).} On the vector space $\mathbb{R}^2$, define $\|(x,y)\| := 2|x| + |y|$ for all $(x,y) \in \mathbb{R}^2$.
\begin{enumerate}[label=(\alph*), leftmargin=*]
    \item Prove that $\|\cdot\|$ is a norm on $\mathbb{R}^2$.
    \item Describe and draw a diagram of the closed unit ball $\overline{B(0,1)}$ in the normed vector space $(\mathbb{R}^2, \|\cdot\|)$.
\end{enumerate}

\vspace{0.2cm}
\noindent \textbf{Problem 2 (3.0 points).} Let $X = C([0,1])$ be the space of continuous mappings $f : [0,1] \to \mathbb{R}$. For each $f \in X$, define $\|f\| = \max_{t \in [0,1]} |f(t)|$. Consider the mapping $T : X \to X$ given by $(Tf)(x) = x \int_0^1 y^2 f(y) dy$.
\begin{enumerate}[label=(\alph*), leftmargin=*]
    \item Prove that $T$ is a continuous linear mapping on $X$.
    \item Find $\|T\|_{B(X,X)}$, where $B(X,X)$ is the space of continuous linear mappings from $X$ to $X$.
\end{enumerate}

\vspace{0.2cm}
\noindent \textbf{Problem 3 (3.0 points).} Consider the space $\mathbb{R}^4$ with the Euclidean norm $\|(x_1, x_2, x_3, x_4)\| = \sqrt{x_1^2 + x_2^2 + x_3^2 + x_4^2}$ for all $x = (x_1, x_2, x_3, x_4) \in \mathbb{R}^4$. Let $M = \{(x_1, x_2, x_3, x_4) \in \mathbb{R}^4 : x_1 - x_2 = 0, x_2 - 2x_3 = 0, x_3 + x_4 = 0\}$ and the functional $f : M \to \mathbb{R}$ defined by $f(x_1, x_2, x_3, x_4) = x_1 + x_2 - x_3 + 2x_4$ for all $x \in M$.
\begin{enumerate}[label=(\alph*), leftmargin=*]
    \item Prove that $f$ is a continuous linear functional on $M$.
    \item Prove that there exists a continuous linear functional $F : \mathbb{R}^4 \to \mathbb{R}$ such that $F|_M = f$ and $\|F\|_{B(\mathbb{R}^4, \mathbb{R})} = \|f\|_{B(M, \mathbb{R})}$. Find the explicit formula of the operator $F$.
\end{enumerate}

\vspace{0.2cm}
\noindent \textbf{Problem 4 (1.0 point).} Consider the Hilbert space $H = L^2([-1, 1])$ with the inner product $\langle f,g \rangle = \int_{-1}^1 f(x)g(x)dx$. Let $M_e$ and $M_o$ denote the sets of even and odd functions in $H$, respectively.
\begin{enumerate}[label=(\alph*), leftmargin=*]
    \item Prove that $M_e$ and $M_o$ are two mutually orthogonal subspaces of $H$.
    \item Consider the function $f(x) = x^3 + 3x^2 - 2x + 1$. Find the orthogonal projection of $f$ onto the subspace $M_o$ and calculate the distance from $f$ to $M_o$.
\end{enumerate}

\vspace{0.5cm}
\begin{center}
\textbf{- END -}
\end{center}

\newpage
